What It Takes to Create with Domain-Appropriate Tools

### 2020-05-28 convivial-2020/acm-style/manuscript-acm.tex
IT JUST WON'T STAY DEAD ... KEEPS COMING BACK!! pls accept now thx

\newcommand{\OROM}{Id}
\title{What it takes to create with domain-appropriate tools}
\subtitle{Reflections on implementing the ``Id{}'' system}
\author[ ]{Joel Jakubovic}
\affiliation[ ]{University of Kent, Canterbury}

@@

What follows in this paper is an account of how I went about building
Id, atop a preliminary ``box'' substrate.
Section\textasciitilde{}\ref{the-id-system} gives an overview of Id.
Section\textasciitilde{}\ref{typical-requirements-of-common-software}
discusses the work involved in obtaining said domain-appropriate
substrate, and Section\textasciitilde{}\ref{patterns-and-polyfilling}
continues with an interpretation of the labour costs of doing this. In
Section\textasciitilde{}\ref{the-id-system-as-a-part-of-the-solution},
we return to the Id system and its role in supporting flexible software.
Section\textasciitilde{}\ref{conclusions-and-future-work} addresses the
question in the title\footnote{The original title of this paper was
  ``What does it take to create with domain-appropriate tools?'', but it
  had to be changed for technical reasons.}, and concludes with next
steps for the project.

@@

\hypertarget{id-as-html-tables}{%
\subsection{Id as HTML tables}\label{id-as-html-tables}}

@@

\hypertarget{the-radical-concept-of-arrows-that-stay-on-the-shapes}{%
\subsubsection{The Radical Concept of Arrows That Stay On The
Shapes}\label{the-radical-concept-of-arrows-that-stay-on-the-shapes}}

@@

\hypertarget{id-as-svg-trees}{%
\subsection{Id as SVG trees}\label{id-as-svg-trees}}

@@

\hypertarget{typical-requirements-of-common-software}{%
\section{Typical Requirements Of Common
Software}\label{typical-requirements-of-common-software}}

@@

\hypertarget{basic-assumptions-about-physical-objects}{%
\subsection{Basic Assumptions About Physical
Objects}\label{basic-assumptions-about-physical-objects}}

@@

\hypertarget{maintaining-relationships-over-time}{%
\subsection{Maintaining Relationships Over
Time}\label{maintaining-relationships-over-time}}

@@

\hypertarget{nut-cracking-with-sledgehammers}{%
\subsection{Nut-Cracking With
Sledgehammers}\label{nut-cracking-with-sledgehammers}}

@@

\hypertarget{wrapping-and-user-data}{%
\subsection{Wrapping and ``user data''}\label{wrapping-and-user-data}}

@@

\hypertarget{context-appropriate-ontologies}{%
\subsection{Context-appropriate
ontologies}\label{context-appropriate-ontologies}}

@@

\hypertarget{the-id-system-as-a-part-of-the-solution}{%
\section{The Id system as a part of the
solution}\label{the-id-system-as-a-part-of-the-solution}}

@@

\hypertarget{minimal-descriptions}{%
\subsection{Minimal descriptions}\label{minimal-descriptions}}

@@

\hypertarget{self-implementation}{%
\subsection{Self-implementation}\label{self-implementation}}

@@

\hypertarget{conclusions-and-future-work}{%
\section{Conclusions and future
work}\label{conclusions-and-future-work}}

\hypertarget{what-did-it-take-and-why}{%
\subsection{What did it take, and why?}\label{what-did-it-take-and-why}}

@@

\hypertarget{what-next}{%
\subsection{What next?}\label{what-next}}

>>>>

\newcommand{\OROM}{Id}
\title{What It Takes to Create with Domain-Appropriate Tools}
\subtitle{Reflections on Implementing the ``Id{}'' System}
\author{Joel Jakubovic}
\affiliation{University of Kent, Canterbury, UK}
\email{jdj9@kent.ac.uk}

@@

What follows in this paper is an account of how I went about building
Id, atop a preliminary ``box'' substrate.
Section\textasciitilde{}\ref{the-id-system} gives an overview of Id.
Section\textasciitilde{}\ref{typical-requirements-of-common-software}
discusses the work involved in obtaining said domain-appropriate
substrate, and Section\textasciitilde{}\ref{patterns-and-polyfilling}
continues with an interpretation of the labour costs of doing this. In
Section\textasciitilde{}\ref{the-id-system-as-a-part-of-the-solution},
we return to the Id system and its role in supporting flexible software.
Section\textasciitilde{}\ref{conclusions-and-future-work} addresses the
question in the title,\footnote{The original title was ``What Does It
  Take to Create with Domain-Appropriate Tools?'', but it has been
  changed for technical reasons.} and concludes with next steps for the
project.

@@

\hypertarget{id-as-html-tables}{%
\subsection{Id as HTML Tables}\label{id-as-html-tables}}

@@

\hypertarget{the-radical-concept-of-arrows-that-stay-on-the-shapes}{%
\subsubsection{The Radical Concept of Arrows that Stay on the
Shapes}\label{the-radical-concept-of-arrows-that-stay-on-the-shapes}}

@@

\hypertarget{id-as-svg-trees}{%
\subsection{Id as SVG Trees}\label{id-as-svg-trees}}

@@

\hypertarget{typical-requirements-of-common-software}{%
\section{Typical Requirements of Common
Software}\label{typical-requirements-of-common-software}}

@@

\hypertarget{basic-assumptions-about-physical-objects}{%
\subsection{Basic Assumptions about Physical
Objects}\label{basic-assumptions-about-physical-objects}}

@@

\hypertarget{maintaining-relationships-over-time}{%
\subsection{Maintaining Relationships over
Time}\label{maintaining-relationships-over-time}}

@@

\hypertarget{nut-cracking-with-sledgehammers}{%
\subsection{Nut-Cracking with
Sledgehammers}\label{nut-cracking-with-sledgehammers}}

@@

\hypertarget{wrapping-and-user-data}{%
\subsection{Wrapping and ``User Data''}\label{wrapping-and-user-data}}

@@

\hypertarget{context-appropriate-ontologies}{%
\subsection{Context-Appropriate
Ontologies}\label{context-appropriate-ontologies}}

@@

\hypertarget{the-id-system-as-a-part-of-the-solution}{%
\section{The Id System as a Part of the
Solution}\label{the-id-system-as-a-part-of-the-solution}}

@@

\hypertarget{minimal-descriptions}{%
\subsection{Minimal Descriptions}\label{minimal-descriptions}}

@@

\hypertarget{self-implementation}{%
\subsection{Self-Implementation}\label{self-implementation}}

@@

\hypertarget{conclusions-and-future-work}{%
\section{Conclusions and Future
Work}\label{conclusions-and-future-work}}

\hypertarget{what-did-it-take-and-why}{%
\subsection{What Did It Take, and Why?}\label{what-did-it-take-and-why}}

@@

\hypertarget{what-next}{%
\subsection{What Next?}\label{what-next}}
